\section{Transition of Databases}

Now we are done with the preliminaries, we can start introducing the framework constructed by \cite{main-result}.
The work puts everything in terms of databases, so we first develop a key piece of terminology.

\begin{defn}[Database Property]
	A \emph{database property} on $\cD$ is a subset $\sfP\subseteq\cD$ of the set of databases $D$.
\end{defn}

We think of $\sfP$ as a predicate for any database $D\in\cD$.
That is, $D\in\sfP$ if and only if $D$ satisfies $\sfP$.
Moreover, by abuse of notation, we also use $\sfP$ as a projector on the space of databases.
As a projector, $\sfP$ leaves databases satisfying it unchanged, and maps databases not satisfying it to $0$.
$$
\sfP(D) = \begin{cases}
	D & \mbox{if } D\in\sfP \\
	0 & \mbox{if } D\notin\sfP
\end{cases}
$$

Now that we have defined database properties, we can then describe the evolution of a database by modeling the \emph{transition} between database properties.
Mathematically, we first introduce the parameter $k$ which models how many parallel processors does the cheating prover have.
We can then define two quantities.
The first of which measures how likely it is that a database that satisfies $\mathsf{P}$
turns into a database that satisfies $\mathsf{P}'$ from a $k$-parallel query.
The second one measures how likely it is that a database that satisfies $\mathsf{P}$
turns into one that satisfies $\mathsf{P}'$ from a quantum algorithm performing $k$-parallel queries up to $q$ times.

\begin{defn}[Database transition capacity]
	Let $k\in\bbN, \sfP, \sfP'\subseteq\cD$. The \emph{transition capacity} is defined as
	$$\lBrack \sfP \xrightarrow{k} \sfP'\rBrack = \max_{x, y} \norm{\sfP' cO_{xy} \sfP}$$
	Furthermore, we define
	$$\lBrack\sfP\xRightarrow{k,q}\sfP']\rBrack:=\sup_{U_i}\norm{\sfP' cO^k U_{q-1} cO^k\ldots U_1 cO^k \sfP}$$
\end{defn}

The two quantities are related by the following bound:
\begin{lem}
	\label{transition-multi-to-single}
	For any sequence of properties $\sfP_i$,
	$$\lBrack\neg \sfP_0\xrightarrow{k, q}\sfP_q]\rBrack
	\leq\sum_{i}\lBrack\neg \sfP_{i-1}\xrightarrow{k}\sfP_i\rBrack$$
\end{lem}

Before proving the bound, we first demonstrate it in action.
As an example, we want to show that it is unlikely to create a hash chain of length $q+1$ using only $q$ queries.
Take
$$\sfP_s=\mathsf{CHN}^{s+1}$$
as the collection of databases containing hash chains of length $s+1$,
then our goal is to bound
$$\lBrack\sfP_0\xRightarrow{k,q}\sfP_q\rBrack.$$
Using the lemma above, it is suffice to bound each of
$$\lBrack\neg \sfP_{i-1}\xrightarrow{k}\sfP_i\rBrack.$$
Intuitively speaking, we have simplified thhe problem to showing that it is difficult to go from chain length $i$ to length $i+2$ in a single query.
We will present later other formula to bound such quantities.
We first present the proof of the lemma.

\begin{proof}
	We first expand the definition of the transition capacity and insert the term $\mathsf{P}_{q-1}+(I-\mathsf{P}_{q-1}$ which equals to the identity.
	The expression can then be simplified using basic properties of operator norm.
	\begin{align*}
		\lBrack\neg \mathsf{P}_0\xRightarrow{k,q}\mathsf{P}_q\rBrack
			&=\sup_{U_i}\norm{\mathsf{P}_q cO^k U_{q-1} cO^k\ldots U_1 cO^k (I-\mathsf{P}_0)} \\
			&=\sup_{U_i}\norm{\mathsf{P}_q cO^k (\mathsf{P}_{q-1}+(I-\mathsf{P}_{q-1})) U_{q-1} cO^k\ldots U_1 cO^k (I-\mathsf{P}_0)}\\
			&\leq\sup_{U_i}\norm{\mathsf{P}_q cO^k \mathsf{P}_{q-1} U_{q-1} cO^k\ldots U_1 cO^k (I-\mathsf{P}_0)}\\
			&\qquad+\sup_{U_i}\norm{\mathsf{P}_q cO^k (I-\mathsf{P}_{q-1}) U_{q-1} cO^k\ldots U_1 cO^k (I-\mathsf{P}_0)}\\
			&\leq\sup_{U_i} \norm{\mathsf{P}_{q-1} cO^k\ldots U_1 cO^k (I-\mathsf{P}_0)}+\sup_{U_i} \norm{\mathsf{P}_q cO^k (I-\mathsf{P}_{q-1})}\\
			&\leq\lBrack\neg \mathsf{P}_0\xRightarrow{k,q-1}\mathsf{P}_{q-1}\rBrack+[\![\neg \mathsf{P}_{q-1}\xrightarrow{k}\mathsf{P}_q]\!]
	\end{align*}
	The result follows from induction.
\end{proof}

Moreover, recall that in the example earlier with finding a $q+1$-chain,
we implicitly related the success probability of an algorithm with the contents of the corresponding database.
Now we also state the connection more precisely by rephrasing a previous result from \cite{compressed-oracles} in the language of databases.
\begin{thm}
	Let $R\subseteq X^\ell\times Y^\ell$ be a relation.
	Let $\mathcal{A}$ be some algorithm that, with success probability $p$, outputs $(\vec{x}, \vec{y})\in R$ where $H(x)=y$.
	Then we have
	$$\sqrt{p}\leq\lBrack\bot\xRightarrow{k, q} \mathsf{P}^R\rBrack+\sqrt{\frac{\ell}{M}}$$
	where $\mathsf{P}^R=\set{D | D\cap R\ne\emptyset}$.
\end{thm}

Now we finally introduce ways to break down and bound quantities of the form 
$$\lBrack\sfP_0\xRightarrow{k,q}\sfP_q\rBrack.$$
To begin, we introduce some more terminology to help us describe database transitions.
\begin{defn}[Recognizability]
	A transition $\neg\mathsf{P}\rightarrow\mathsf{P}'$ is strongly and uniformly \emph{recognizable}
		by $\set{\mathsf{L}_i}$ if and only if $\mathsf{P}'\subseteq \cup_i\set{\mathsf{L}_i}\subseteq\mathsf{P}$.
\end{defn}

For this definition, it is easier to first consider the $\sfP=\sfP'$ case.
In that case, $\mathsf{P}=\cup_i\set{\mathsf{L}_i}$ just gives us $\sfP=\sfP'$.
$\neg\mathsf{P}\rightarrow\mathsf{P}'$ just gives us $\mathsf{P}=\cup_i\set{\mathsf{L}_i}$,
which in turn says that for any $D$ to satisfy $\mathsf{P}$, it is necessary and sufficient that $D$ satisfies one of the $\mathsf{L}_i$'s.
In particular, it is always true that $\set{P}$ recognizes $\neg\sfP\rightarrow\sfP$,
though this fact is not useful in the later steps.

There are other versions such as \emph{weak} or \emph{non-uniform} recognizabilities which we will unfortunately skip in the interest of time.
We can now bound transition capabilities in terms of \emph{local} properties that recognize said transition.
Roughly speaking, a set of database properties $\set{\mathsf{L}_i}$ is local if the truth value of each $\mathsf{L}_i$ depends only on a constant number of $x_i$'s.

\begin{thm}
	\label{property-to-bound}
	Let $\mathsf{L}_i$ be local properties that strongly recognize $\neg\mathsf{P}\rightarrow\mathsf{P}'$, then we have
	$$[\![\mathsf{P}\xrightarrow{k}\mathsf{P}']\!]\leq\max_{x, D}\sqrt{10\sum_iP[U\in\mathsf{L}_i]}$$
	where $U$ is the uniform distribution.
\end{thm}

One highlight of this theorem is that the right-hand side is entirely classical.
In other words, this framework allows its users to analyze certain algorithms against quantum adversaries using almost fully classical reasoning,
and the resulting analysis may even roughly follow that of a classical adversary.
Towards that goal, now we present a few formula to break down transition capacities.
First, we have a formula that we can use to ``remove" some pathological low-probability event $\neg\mathsf{Q}$ such as hash collisions.
\begin{lem}
	$$
	\lBrack\sfP\xrightarrow{k}\sfP''\rBrack\leq
	\lBrack\sfP\xrightarrow{k} \sfP''\setminus Q\rBrack+
	\lBrack\sfP\xrightarrow{k} \sfP''\cap Q\rBrack.
	$$
\end{lem}
Next, we have an analogue for union bounds.
\begin{lem}
For all properties $P, Q, \sfP''$,
$$
	\lBrack\sfP\xrightarrow{k}\sfP''\rBrack\leq
	\lBrack\sfP\xrightarrow{k} \sfP''\setminus Q\rBrack+
	\lBrack\sfP\xrightarrow{k} \sfP''\cap Q\rBrack.
$$
\end{lem}
Lastly, we also have a way to break the queries down by splitting the domain $X=X_1\cup X_2$.
Here we define $\lBrack\sfP\xrightarrow{k} \sfP''|X\rBrack$ similarly to $\lBrack\sfP\xrightarrow{k} \sfP''\rBrack$,
except with extra constraints on the oracle input that $x\in X$.
\begin{lem}
$$
	\lBrack\sfP\xrightarrow{k} \sfP''|X\rBrack\leq
	\lBrack\sfP\xrightarrow{k} P'|X'\rBrack+
	\lBrack\neg P'\xrightarrow{k} \sfP''|X''\rBrack.
$$
\end{lem}
This last formula is especially helpful to analyze protocols that use the construction
\begin{align*}
	H_1&=H(1, x) \\
	H_2&=H(0, x)
\end{align*}
to implement two hash functions from a single hash function.
We will show its proof:
\begin{proof}
	Decompose
	$$cO_{x,y}=cO_{x',y'}cO_{x'',y''}$$
	so that $cO_{x',y'}$ acts on all $x\in X'$.
	Then we have
\begin{align*}
	\lBrack P\xrightarrow{k} P''|X\rBrack &=\max_{xy}\norm{P''cO_{xy}P}\\
			&=\max_{xy}\norm{P''cO_{x''y''}cO_{x'y'}P}\\
			&=\max_{xy}\norm{P''cO_{x''y''}(P' + (I - P'))cO_{x'y'}P}\\
			&=\max_{xy}\norm{P''cO_{x''y''}P' cO_{x'y'}P}
			+\max_{xy}\norm{P''cO_{x''y''}(I - P')cO_{x'y'}P}\\
			&=\max_{xy}\norm{P' cO_{x'y'}P}
			+\max_{xy}\norm{P''cO_{x''y''}(I - P')}\\
			&\leq
			\lBrack P\xrightarrow{k} P'|X'\rBrack +
			\lBrack \neg P'\xrightarrow{k} P''|X''\rBrack .
\end{align*}
\end{proof}

We can simplify a transition capacity using these formula.
With a simple enough transition capacity,
we might be able to identify local properties that recognize it.
Once we do, we can then apply \Cref{property-to-bound} to obtain a bound.

As an example, we will give a rough sketch of the analysis of the proof of sequential work.
